Bow shocks, bow waves, and dust waves

### 2017-12-21 papers/Papers1234/sec-dust-bow-intro.tex
Revisit the ionization front trapping
Take into account hardening.  And calculate the dust and gas optical
depths separately for the shocked shell

>>>>

\subsection{Radiative cooling lengths}
\label{sec:radi-cool-lengths}

\subsection{Ionization state of the bow shell}
\label{sec:trapp-ioniz-front}

\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
\newcommand\shell{\ensuremath{_{\text{sh}}}}

We wish to calculate whether the star is capable of photoionizing the
entire bow shock shell, or whether the ionization front will be trapped
within it.  The number of hydrogen recombinations per unit time per
unit area in a fully ionized shell is \(\mathcal{R} = \alphaB n\shell^2 h\shell\),
while the flux of ionizing photons incident on the inner edge of the
shell is \(\mathcal{F} = S / 4 \pi R_0^2\).  Assuming photoionization equilibrium, the hydrogen photoabsorption optical depth of the shell is
\begin{equation}
  \label{eq:ion-tau-gas}
  \tau\gas = - \ln(1 - \mathcal{R} / \mathcal{F}) \ .
\end{equation}
The column density of the shocked shell can be found, for example, from equations~(10) and~(12) of \citet{Wilkin:1996a} in the limit \(v/V \to 0\) (Wilkin's parameter \(\alpha\)) and \(\theta \to 0\).  This yields
\begin{equation}
  \label{eq:shocked-shell-column}
  n\shell h\shell = \tfrac34 n R_0 \ .
\end{equation}
